Substructure Boosts to Dark Matter Annihilation from Sommerfeld Enhancement

### 2009-04-16 tex/response.txt

Dear Editor,

Please find below the response to the referees' comments for the
submission "Substructure boosts to dark matter annihilation from
Sommerfeld enhancement" by myself (submission # DC10513).

I have made changes following the referee's suggestions and have also
update figures 1, 2, 5, 6, and 7 to make the label in these plots more
clear to the reader.

A detailed list of the changes is:

- I slightly rewrote the paragraph containing Eq. 20 to include the
definition of the virial radius;

- I fixed a type which the referee found in the paragraph below Eq. 39;

- I changed the color of the label in figures 1, 2, 5, 6, and 7 from
  black to white;

- I enlarged figures 9, 10, 12, 14, arranging the two panels now below
  each other. I updated the caption of figure 10 to reflect this
  change.

Please contact me by the information given below with any questions
regarding this re-submission.

With kind regards,

Jo Bovy

-
Jo Bovy
Ctr. for Cosmology & Particle Physics, 
Dept. of Physics
New York University
4 Washington Place
New York, NY 10003
jb2777@nyu.edu

In what follows the referee's comments are indented.

==================================================================

	Dear Dr. Bovy:

	The manuscript ``Substructure boosts to dark matter
	annihilation from Sommerfeld enhancement'' (dc10513) by Bovy,J
	has been reviewed by one of our referees.  Comments from the
	report are enclosed for your consideration.

	When you resubmit your manuscript, please include a summary of
	the changes made, and a brief response to all recommendations
	and criticisms.

	Sincerely,

	Rashmi Ray
        Senior Assistant Editor
        Physical Review D

	----------------------------------------------------------------
	Report:
	----------------------------------------------------------------
	This is a very good paper. It makes a careful, intelligent
	contribution to the hot topic of boost factors in Galactic
	dark matter annihilation.  I am also impressed with the
	clarity of exposition.

	I have two small suggestions and a typo to convey to the
	author, for his/her optional consideration.

	1. Typo: toward the end of the paragraph following Eq 39, an
           enhancement of 10^-2 is reported; I believe the author
           means 10^+2.

That is correct, I did mean 10^+2. This has been corrected in the text.

	2. In Eq 20, the virial radius r_vir is used; I don't
	   believe it is defined in the text.

I have added the definition of the virial radius in the paragraph
containing Eq.20 before the definition of the concentration. I have
also moved up the definition of the virial mass from where it was
before (it used to be at the end of that same paragraph).

	3. Figs 9, 10, 12, 14 are too small in the copy I received
	   from APS.  Perhaps this is not the author's issue.

This was my fault. I have replaced these figures with larger versions.
-------------------------------------------------------------------------

### 2009-04-17 tex/somm.tex
sommboost: forgot a ,

We have not discussed the substructure boost to the \DM\ annihilation
signal from unresolved substructure in the Galactic halo. This is,
however, interesting in the light of the Sommerfeld enhancement, since
it might lead to a different prediction about the relative magnitudes
of the annihilation signal coming from the resolved Galactic halo and
unresolved halo, as well from the resolved substructures in the
Galactic halos. It is already clear that in the generic 1/$v$
Sommerfeld enhancement the main halo, with its typical velocity
dispersion of $\sim\!150$ km s$^{-1}$, will receive a much smaller
enhancement than the \dSphs, with their typical velocity dispersions
of 10 km s$^{-1}$. This, however, ignores the effects of saturation
and resonances, which might be important in the specific particle
physics model adopted for the Sommerfeld enhancement. Additionally,
while the velocity dispersion of the Galactic halo might be of the
order of 100 km s$^{-1}$ the actual velocity dispersion relevant to
the Sommerfeld enhancement might be much smaller for halo \DM\
particles. If a large fraction of the \DM\ in the Galactic halo is
part of a cold stream ---and various numerical simulations predict
that large parts of the halo, if not all of the halo, is made up of
such cold streams with typical velocity dispersions of the order of 1
km s$^{-1}$ \cite{1999MNRAS.307..495H,2003MNRAS.339..834H}--- then the
relevant relative velocity of \DM\ particles is set by the velocity
dispersion of particles in the stream, and not by the velocity
dispersion of the streams in the halo, which is what the 100 km
s$^{-1}$ Galactic halo velocity dispersion corresponds to in these
scenarios. Thus, the expected \DM\ annihilation signal from the main
halo could be much larger than that naively expected for a halo with a
velocity dispersion of 100 km s$^{-1}$.

>>>>

We have not discussed the substructure boost to the \DM\ annihilation
signal from unresolved substructure in the Galactic halo. This is,
however, interesting in the light of the Sommerfeld enhancement, since
it might lead to a different prediction about the relative magnitudes
of the annihilation signal coming from the resolved Galactic halo and
unresolved halo, as well from the resolved substructures in the
Galactic halos. It is already clear that in the generic 1/$v$
Sommerfeld enhancement the main halo, with its typical velocity
dispersion of $\sim\!150$ km s$^{-1}$, will receive a much smaller
enhancement than the \dSphs, with their typical velocity dispersions
of 10 km s$^{-1}$. This, however, ignores the effects of saturation
and resonances, which might be important in the specific particle
physics model adopted for the Sommerfeld enhancement. Additionally,
while the velocity dispersion of the Galactic halo might be of the
order of 100 km s$^{-1}$, the actual velocity dispersion relevant to
the Sommerfeld enhancement might be much smaller for halo \DM\
particles. If a large fraction of the \DM\ in the Galactic halo is
part of a cold stream ---and various numerical simulations predict
that large parts of the halo, if not all of the halo, is made up of
such cold streams with typical velocity dispersions of the order of 1
km s$^{-1}$ \cite{1999MNRAS.307..495H,2003MNRAS.339..834H}--- then the
relevant relative velocity of \DM\ particles is set by the velocity
dispersion of particles in the stream, and not by the velocity
dispersion of the streams in the halo, which is what the 100 km
s$^{-1}$ Galactic halo velocity dispersion corresponds to in these
scenarios. Thus, the expected \DM\ annihilation signal from the main
halo could be much larger than that naively expected for a halo with a
velocity dispersion of 100 km s$^{-1}$.
